A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

The PCS is a slightly challenging to visualize because it represents projections which are embedded in the SVD/HOSVD factors of the original permeability field. An aid for visualizing the PCS for a 2D permeability field is to write out the $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or SVD factors) and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{V^{\intercal}}$) as separate PCS. A similar intuition can be extended to HOSVD for 3D permeability fields. The decomposition of a matrix into its factors using SVD  \cite{Cline_2007, Tharwat_2016} or HOSVD \cite{Kolda_2009, Lathauwer_2000} is covered in details in several published materials. However, for completeness, the appendix contains a brief introduction to SVD (\ref{subsection:svd_brief}) and HOSVD (\ref{subsection:hosvd_brief}).

>>>>

The PCS is a particularly challenging to visualize because it represents projections which are embedded in the SVD/HOSVD factors of the original permeability field. An aid for visualizing the PCS for a 2D permeability field is to write out the $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or SVD factors) and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{V^{\intercal}}$) as separate PCS. A similar intuition can be extended to HOSVD for 3D permeability fields. The decomposition of a matrix into its factors using SVD  \cite{Cline_2007, Tharwat_2016} or HOSVD \cite{Kolda_2009, Lathauwer_2000} is covered in details in several published materials. However, for completeness, the appendix contains a brief introduction to SVD (\ref{subsection:svd_brief}) and HOSVD (\ref{subsection:hosvd_brief}).
